Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-20 outputs/paper/paper.Rmd
survey

>>>>

```{r echo=FALSE, out.width='50%'}
# insert pictures of survey questions
include_graphics(paste(getwd(),"/inputs/survey/survey1.png", sep = ""))
include_graphics(paste(getwd(),"/inputs/survey/survey2.png", sep = ""))
include_graphics(paste(getwd(),"/inputs/survey/survey3.png", sep = ""))
include_graphics(paste(getwd(),"/inputs/survey/survey4.png", sep = ""))
```
